Approximating the Number of COVID-19 Infections in the United States Across 2021

### 2023-06-30 writing/manuscript.Rmd
update manuscript

@@

In Figure \@ref(fig:ratio-estimated-to-observed-by-wave), we consider three distinct two-week intervals during waves of the pandemic in 2021. Simulation intervals for all two-week intervals for all states are shown in Supplementary Figure sim-intervals-state.

Several states consistently have among the highest or lowest ratios of estimated to observed infections. In particular, there are 6 states with among the lowest 10 ratios of estimated infections to observed infections, and as such the highest case ascertainment, for more than 80% of time intervals considered. These states were Rhode Island, Massachusetts, District of Columbia, Alaska, New York, and Vermont. Meanwhile, states that had the highest ratios, and equivalently the lowest case ascertainment, include Mississippi, South Dakota, Oklahoma, Nebraska, and Tennessee.

>>>>

In Figure \@ref(fig:ratio-estimated-to-observed-by-wave), we consider three distinct two-week intervals during waves of the pandemic in 2021.

Several states consistently have among the highest or lowest ratios of estimated to observed infections. In particular, there are 6 states with among the lowest 10 ratios of estimated infections to observed infections, and as such the highest case ascertainment rates, for more than 80% of time intervals considered. These states were Rhode Island, Massachusetts, District of Columbia, Alaska, New York, and Vermont. Meanwhile, states that had the highest ratios, and equivalently the lowest case ascertainment rates, include Mississippi, South Dakota, Oklahoma, Nebraska, and Tennessee.

In Figure \@ref(fig:simulation-intervals-state), we see the simulation intervals for all two-week intervals and all states.

```{r simulation-intervals-state, fig.cap="Simulation intervals for each 2-week interval considered, for all states. For any given state, each vertical bar shows the 2.5\\% percentile and 97.5\\% percentile for the total number of infections in that two-week interval. Covidestim intervals summed over the same two-week time-scale are shown in red. The scale on the $y$-axis is distinct across states to highlight differences across time within each state."}

include_graphics(here('figures/intervals-and-covidestim-all-states.pdf'))

@@
